Rapid Epidemiological Analysis of Comorbidities and Treatments in COVID-19 in Scotland (REACT-SCOT): a case-control study based on the Scottish population [**Draft, not to be quoted**]

### 2020-05-17 Covid_ethnicity_Scotland.Rmd
fixed ethnicity table

rownames(table.hospitalized.demog) <- gsub("_", " ", rownames(table.hospitalized.demog))
knitr::kable(table.demog.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="onomap.hosp",
             col.names=c(clean.header(colnames(table.hospitalized.demog)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of hospitalized disease with demographic variables including ethnicity based on name classification") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2))  %>%
    kable_styling(latex_options="hold_position") %>% 
    column_spec(column=1, width="2.7cm") %>%
    column_spec(column=2, width="2cm")  %>%
    column_spec(column=3, width="1.85cm")  %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.5cm") %>%
    column_spec(column=6, width="2.5cm") %>%
    column_spec(column=7, width="1.5cm")

>>>>

rownames(table.hospitalized.demog) <- gsub("_", " ", rownames(table.hospitalized.demog))
knitr::kable(table.hospitalized.demog,
             escape=FALSE, 
             booktabs=TRUE,
             label="onomap.hosp",
             col.names=c(clean.header(colnames(table.hospitalized.demog)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of hospitalized disease with demographic variables including ethnicity based on name classification") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2))  %>%
    kable_styling(latex_options="hold_position") %>% 
    column_spec(column=1, width="2.7cm") %>%
    column_spec(column=2, width="2cm")  %>%
    column_spec(column=3, width="1.85cm")  %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.5cm") %>%
    column_spec(column=6, width="2.5cm") %>%
    column_spec(column=7, width="1.5cm")

### 2020-05-17 casecontrol.Rmd
fixed ethnicity table

## Matched controls
For each test-positive case, we ascertained ten matched controls of the same sex, one year age band and attending the same General Practice as each case alive on the same day as the date of test in the case using the Community Health Index (CHI) database. As this is an incidence density sampling design, it is possible and correct for an individual to appear in the dataset more than once, initially as a control and subsequently as a case.  With this design, odds ratios in conditional logistic regression models are equivalent to rate ratios.  The odds ratios based on the conditional likelihood will differ from the unconditional odds ratios calculable from the frequencies of exposure in cases and controls [@breslow_estimation_1978]

@@

## Morbidity and drug prescribing
For all cases and controls, ICD-10 diagnostic codes were extracted from the last five years of hospital discharge records in the Scottish Morbidity Record (SMR01), excluding records of discharges less than 25 days before testing positive for SARS-Cov-2 and using all codes on the discharge. British National Formulary  (BNF) drug codes were extracted from the last year of encashed prescriptions, excluding those encashed less than 25 days before testing positive for SARS-CoV-2.  Diagnosed cases of diabetes were identified through linkage to the national diabetes register (SCI-Diabetes), with a clinical classification of diabetes type as Type 1, Type 2 or Other.

@@

## Statistical methods
To estimate the relation of cumulative incidence and mortality from COVID-19 to age and sex, logistic regression models were fitted to the proportions of cases and non-cases in the Scottish population, using the estimated population of Scotland in mid-year 2019 which are available by one-year age group up to age 90 years. For the case-control study, estimates of associations with severe COVID-19 were based on conditional logistic regression, implemented as Cox regression in the R function `survival::clogit`.  Among those cases and controls without any of the pre-defined conditions we then further examined associations of ICD-10 and BNF chapter with severe COVID-19. Where the sample of cases and controls is restricted, this will generate strata that contain no cases.  These strata will be ignored by the conditional logistic regression model as they do not contribute to the conditional likelihood.

To construct risk prediction models, we used stepwise regression alternating between forward and backward steps to maximize the AIC, implemented in the R function `stats::step`.  The performance of the risk prediction model as a classifier was examined by 4-fold cross-validation, with performance calculated over all test folds as the expected information for discrimination $\Lambda$ [@mckeigue_quantifying_2019] and (more conventionally) as the C-statistic. The rationale for using $\Lambda$ to quantify the predictive performance of a binary classifier has been explained elsewhere [@mckeigue_quantifying_2019].  Especially relevant to this study is that the contributions of independent predictors are additive on the scale of $\Lambda$.  We can thus add the information for discrimination conditional on age and sex (estimated from this matched case-control study) to the information for discrimination estimated from a logistic regression model on age and sex in the general population.

@@

This estimate of `r table.densities[3, 5] ` bits for the information conditional on age and sex obtained from the matched case-control study can be added to the information for discrimination `r round(cases.Lambda.agesex, 2)` bits obtained from the logistic regression on age and sex in the population using age and sex to estimate the total information for discrimination of a risk classifier in the population as that would be obtained in the population to give a total of `r table.densities[3, 5] + round(cases.Lambda.agesex, 2)` bits.

Figure \ref{fig:wevid} shows the class-conditional distributions of the weight of evidence $W$ favouring case over control status from the model based on the extended variable set.  This shows, as expected for a multifactorial classifier, that the distributions are approximately Gaussian: there is no clear divide between high-risk and low-risk individuals of the same age and sex. Figure \ref{fig:roc}, which shows the corresponding receiver operating characteristic (ROC) curve, encodes exactly the same information in a different form.  The likelihood ratio $2^W$ at any given sensitivity and specificity is the gradient of the model-based ROC curve.

@@

## Conclusion
In conclusion the epidemiology of severe COVID-19 disease is becoming clearer  and we confirm here the importance of sociodemographic factors and  chronic conditions such as diabetes, asthma, circulatory disease and others. However there is not just one small set of conditions that contribute to risk but many conditions as evidenced by associations across with past medical and prescribing history across many body systems.  As countries attempt to emerge from lockdown whist protecting the most vulnerable multivariate classifiers rather than crude rule-based approaches will be needed to define those most at risk.

# References {-}

@@

knitr::kable(table.demog.aug[, 1:4],
             escape=FALSE, 
             booktabs=TRUE,
             label="demog",
             digits=c(0, 0, 0, 200), 
             col.names=c(clean.header(colnames(table.demog.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Univariate associations of severe disease with demographic factors") %>%
    column_spec(column=1, width="2.5cm") %>%
    column_spec(column=2:4, width="2.5cm") %>%
    group_rows("Ethnicity", 1, 3) %>%
    group_rows("SIMD quintile", 4, 8)

@@

rownames(table.agegr) <- replace.names(rownames(table.agegr))
knitr::kable(table.agegr,
             escape=FALSE, 
             booktabs=TRUE,
             label="agegr",
             align=rep("c", 8), 
             caption="Associations of severe disease with risk factors, by age group") %>%
    column_spec(column=1, width="3.5cm") %>%
    group_rows("Listed condition", 3, nrow(table.agegr) - 1) %>%
    add_header_above(c(" "=1, "0-39 years"=2, "40-59 years"=2,
                       "60-74 years"=2, "75+ years"=2)) %>%
    landscape()

@@

knitr::kable(table.agegr.all,
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.allages",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(table.agegr.all)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions over all age groups") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

rownames(table.conditions.aug) <- gsub("_", " ", rownames(table.conditions.aug))
knitr::kable(table.conditions.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="conditions",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(table.conditions.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with hospital diagnoses in last 5 years, in those without listed conditions") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

rownames(table.drugs.aug) <- gsub("_", " ", rownames(table.drugs.aug))
knitr::kable(table.drugs.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="drugs",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(table.drugs.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with prescribed drugs in those without listed conditions") %>%
    column_spec(column=1, width="4.5cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()
```

@@

rownames(table.densities) <- c("Demographic only",
                               "Demographic + listed conditions",
                               "Extended variable set")

@@

knitr::kable(table.ethnicsmr.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="ethnicsmr",
             digits=c(0, 0, 0, 200), 
             col.names=c(colnames(table.ethnicsmr.aug)[1:2],
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with ethnicity classified in hospital records") %>%
    column_spec(column=1, width="3cm")

@@

knitr::kable(tables.agegr[[1]],
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.lt60",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(colnames(tables.agegr[[1]])[1:2],
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions in those aged less than 60") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

knitr::kable(tables.agegr[[2]],
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.60to74",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(colnames(tables.agegr[[2]])[1:2],
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions in those aged 60-74 years") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

knitr::kable(tables.agegr[[3]],
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.ge75",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(tables.agegr[[3]])[1:2]),
                         "Rate ratio (95\\% CI)", "p-value",
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions in those aged 75 years and over") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

knitr::kable(table.icdsubchapters,
             escape=FALSE, 
             booktabs=TRUE,
			 longtable=TRUE, 
             label="icdsubchapters",
             col.names=c(clean.header(colnames(table.icdsubchapters)[1:2]),
                         "Rate ratio (95\\% CI)", "p-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with hospital diagnoses by ICD subchapters: rows retained are those with p < 0.001 and at least 50 cases and controls") %>%
    column_spec(column=1, width="13cm") %>%
    column_spec(column=2:3, width="1.5cm") %>%
    column_spec(column=5, width="1.5cm") %>%
    landscape()

@@

knitr::kable(retained.full, 
             booktabs=TRUE,
             escape=FALSE,
             label="stepwise",
             col.names=c("log rate ratio", "p-value"), 
             align=rep("c", 2),
             caption="Stepwise regression: variables retained in model for severe disease") %>%
    group_rows("Diabetes", 6, 8)

>>>>

## Matched controls
For each test-positive case, we ascertained ten matched controls of the same sex, one year age band and attending the same General Practice as each case alive on the same day as the date of test in the case using the Community Health Index (CHI) database. As this is an incidence density sampling design, it is possible and correct for an individual to appear in the dataset more than once, initially as a control and subsequently as a case.

@@

## Morbidity and drug prescribing
For all cases and controls, ICD-10 diagnostic codes were extracted from the last five years of hospital discharge records in the Scottish Morbidity Record (SMR01), excluding records of discharges less than 25 days before testing positive for SARS-CoV-2 and using all codes on the discharge. British National Formulary (BNF) drug codes were extracted from the last year of encashed prescriptions, excluding those encashed less than 25 days before testing positive.   Diagnosed cases of diabetes were identified through linkage to the national diabetes register (SCI-Diabetes), with a clinical classification of diabetes type as Type 1, Type 2 or Other.

@@

## Statistical methods
To estimate the relation of cumulative incidence and mortality from COVID-19 to age and sex, logistic regression models were fitted to the proportions of cases and non-cases in the Scottish population, using the estimated population of Scotland in mid-year 2019 which are available by one-year age group up to age 90 years. For the case-control study, estimates of associations with severe COVID-19 were based on conditional logistic regression, implemented as Cox regression in the R function `survival::clogit`.  Among those cases and controls without any of the pre-defined conditions we then further examined associations of ICD-10 and BNF chapter with severe COVID-19. Where the sample of cases and controls is restricted, this will generate strata that contain no cases.  These strata will be ignored by the conditional logistic regression model as they do not contribute to the conditional likelihood.  With incidence density sampling, odds ratios in conditional logistic regression models are equivalent to rate ratios.  These odds ratios based on the conditional likelihood will differ from the unconditional odds ratios calculable from the frequencies of exposure in cases and controls [@breslow_estimation_1978]

To construct risk prediction models, we used stepwise regression alternating between forward and backward steps to maximize the AIC, implemented in the R function `stats::step`.  The performance of the risk prediction model as a classifier was examined by 4-fold cross-validation, with performance calculated over all test folds as the expected information for discrimination $\Lambda$ [@mckeigue_quantifying_2019] and (more conventionally) as the C-statistic. The rationale for using $\Lambda$ to quantify the predictive performance of a binary classifier, and especially to quantify increments in predictive performance, has been explained elsewhere [@mckeigue_quantifying_2019].  The contributions of independent predictors are additive on the scale of $\Lambda$.  In this study we have estimated the information for discrimination provided by age and sex (from a logistic regression model in the general population), and the information for discrimination provided by other risk factors conditional on age and sex (from conditional logistic regression models in this case-control study matched for age and sex).  We can add these to obtain the total information for discrimination that would be obtained with a classifier in the general population.  As described elsewhere, this can be used to estimate the proportion of those destined to develop severe or fatal disease who would be correctly classified as high risk under a shielding policy [@mckeigue_evaluation_2020].

@@

This estimate of `r table.densities[3, 5] ` bits for the information conditional on age and sex obtained from the matched case-control study can be added to the information for discrimination `r round(cases.Lambda.agesex, 2)` bits obtained from the logistic regression on age and sex in the population using age and sex to estimate the total information for discrimination of a risk classifier that would be obtained in the population to give a total of `r table.densities[3, 5] + round(cases.Lambda.agesex, 2)` bits.

Figure \ref{fig:wevid} shows the class-conditional distributions of the weight of evidence $W$ favouring case over control status from the model based on the extended variable set.  The model-based distributions have been adjusted slightly to make them mathematically consistent as described elsewhere [@mckeigue_quantifying_2019].  This shows, as expected for a multifactorial classifier, that the distributions are approximately Gaussian: there is no clear divide between high-risk and low-risk individuals of the same age and sex. Figure \ref{fig:roc}, which shows the corresponding receiver operating characteristic (ROC) curve, encodes exactly the same information as Figure \ref{fig:wevid} in a different form.  The likelihood ratio $2^W$ at any given sensitivity and specificity is the gradient of the model-based ROC curve.

@@

# Conclusion
In conclusion the epidemiology of severe COVID-19 disease is becoming clearer  and we confirm here the importance of sociodemographic factors and  chronic conditions such as diabetes, asthma, circulatory disease and others. However there is not just one small set of conditions that contribute to risk but many conditions as evidenced by associations across with past medical and prescribing history across many body systems.  As countries attempt to emerge from lockdown whist protecting the most vulnerable multivariate classifiers rather than crude rule-based approaches will be needed to define those most at risk.

# References

@@

knitr::kable(table.demog.aug[, 1:4],
             escape=FALSE, 
             booktabs=TRUE,
             label="demog",
             col.names=c(clean.header(colnames(table.demog.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Univariate associations of severe disease with demographic factors") %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="1.8cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    group_rows("Ethnicity", 1, 3) %>%
    group_rows("SIMD quintile", 4, 8)

@@

rownames(table.agegr) <- replace.names(rownames(table.agegr))
table.agegr[1, c(1, 3, 5, 7)] <- " "
knitr::kable(table.agegr,
             escape=FALSE, 
             booktabs=TRUE,
             label="agegr",
             align=rep("c", 8), 
             caption="Associations of severe disease with risk factors, by age group") %>%
    column_spec(column=1, width="3.5cm") %>%
    group_rows("Listed condition", 3, nrow(table.agegr) - 1) %>%
    add_header_above(c(" "=1, "0-39 years"=2, "40-59 years"=2,
                       "60-74 years"=2, "75+ years"=2)) %>%
    landscape()

@@

knitr::kable(table.agegr.all,
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.allages",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(table.agegr.all)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions over all age groups") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

rownames(table.conditions.aug) <- gsub("_", " ", rownames(table.conditions.aug))
knitr::kable(table.conditions.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="conditions",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(table.conditions.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with hospital diagnoses in last 5 years, in those without any listed condition") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

rownames(table.drugs.aug) <- gsub("_", " ", rownames(table.drugs.aug))
knitr::kable(table.drugs.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="drugs",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(table.drugs.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with prescribed drugs in those without any listed condition") %>%
    column_spec(column=1, width="4.5cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()
```

@@

rownames(table.densities) <- c("Demographic only",
                               "Demographic + listed conditions",
                               "Extended variable set")
table.densities[, 6] <- round(table.densities[, 6] - table.densities[1, 6], 1)

@@

knitr::kable(table.ethnicsmr.aug,
             escape=FALSE, 
             booktabs=TRUE,
             label="ethnicsmr",
             digits=c(0, 0, 0, 200), 
             col.names=c(clean.header(colnames(table.ethnicsmr.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with ethnicity classified in hospital records") %>%
    column_spec(column=1, width="3cm")

@@

knitr::kable(tables.agegr[[1]],
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.lt60",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(colnames(tables.agegr[[1]])[1:2],
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions in those aged less than 60") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

knitr::kable(tables.agegr[[2]],
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.60to74",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(colnames(tables.agegr[[2]])[1:2],
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions in those aged 60-74 years") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

knitr::kable(tables.agegr[[3]],
             escape=FALSE, 
             booktabs=TRUE,
             label="listed.conditions.ge75",
             digits=c(0, 0, 0, 200, 0, 200), 
             col.names=c(clean.header(colnames(tables.agegr[[3]])[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with listed conditions in those aged 75 years and over") %>%
    column_spec(column=1, width="4cm") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    landscape()

@@

knitr::kable(table.icdsubchapters,
             escape=FALSE, 
             booktabs=TRUE,
			 longtable=TRUE, 
             label="icdsubchapters",
             col.names=c(clean.header(colnames(table.icdsubchapters)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align=rep("c", 6), 
             caption="Associations of severe disease with hospital diagnoses by ICD subchapters: rows retained are those with p < 0.001 and at least 50 cases and controls") %>%
    column_spec(column=1, width="13cm") %>%
    column_spec(column=2:3, width="1.5cm") %>%
    column_spec(column=5, width="1.5cm") %>%
    landscape()

@@

knitr::kable(retained.full, 
             booktabs=TRUE,
             escape=FALSE,
             label="stepwise",
             col.names=c("log rate ratio", "$p$-value"), 
             align=rep("c", 2),
             caption="Stepwise regression: variables retained in model for severe disease") %>%
    group_rows("Diabetes", 6, 8)
